Do motif roles provide unique information about species risk of extinction?\\ \medskip Supplementary Information

### 2021-09-28 manuscript/supplement_motifs.tex
Added some persistence stuff to SI

\section{Functional response of consumers}
        As well as the intrinsic baseline probability of extinction, extinction risk for consumers is affected by access to resources. 
		When all resources are extant, the probability of extinction for a consumer $i$, $P(\lnot i)$, is equal to the baseline probability; $P(\lnot i|X_{1},...,X_{n}) = \pi_{base}$. 
		When all resources are extinct, the consumer will go extinct; $P(\lnot i|\lnot X_{1},...,\lnot X_{n})=1$.

@@

>>>>

\section{Network creation and processing}

    A Bayesian food web depicts probabilistic relationships among a set of species where each species' probability of persistence depends upon the probabilities of its resource species persisting~\citep{Jensen_Nielsen,Eklof2013}. 
    All persistence calculations therefore begin  by determining the status of the primary producers (who do not depend on other species).
    Calculations continue in a strictly bottom-up manner with primary consumers (who depend only on primary producers), and so on up the network.

    While niche-model food webs can contain cycles (e.g., species A eats B, B eats C, and C eats A), such cycles make it impossible to calculate persistence in the Bayesian network framework~\citep{Tarjan1972}. 
    We therefore removed any cycles within each network by removing the link in each cycle which contributed least to the robustness of the food web, following~\citet{Allesina2009}.
    This is achieved by first finding the set of resources for each consumer and then removing the consumer-resource connections which have the lowest eigenvalue centrality~\citep{Allesina2009}.
    These links have the least effect on the overall stability of the network; removing them creates an acyclic network with very similar properties to the original network.
    Next, we ordered the species from lowest to highest trophic level using a topological sorting routine following \citep{Tarjan1972, Allesinaetal2005}, ensuring that probability calculations follow a strict bottom-up order. 
    After these steps, calculations of persistence probabilities can begin.

\section{Calculating persistence}

    \subsection{Stochastic extinction}

    \subsection{Functional response of consumers}

        As well as the intrinsic baseline probability of extinction, extinction risk for consumers is affected by access to resources. 
		When all resources are extant, the probability of extinction for a consumer $i$, $P(\lnot i)$, is equal to the baseline probability; $P(\lnot i|X_{1},...,X_{n}) = \pi_{base}$. 
		When all resources are extinct, the consumer will go extinct; $P(\lnot i|\lnot X_{1},...,\lnot X_{n})=1$.

@@

    \subsection{Numerical simulation}
